Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-07 paper/disc20clustering.tex
Cascade commented
notations, defs etc.

 \newcommand{\OPT}{\textsf{OPT}\xspace}
 \newcommand{\ALG}{\textsf{ALG}\xspace}
 \newcommand{\PPL}{\textsf{PPL}\xspace}
 \newcommand{\OBRP}{BRP}
 \newcommand{\PPOBRP}{PP-BRP}
 \newcommand{\dist}{\textsf{dist}}
 \newcommand{\TAlg}{{\ensuremath{\textsf{ALG}_{3}}}\xspace}

@@

\section{Bounding the cost of a single reconfiguration of components}

@@

@@

Corollary: Algorithm DET2 is $O(\ell \cdot k \cdot \min \{ \ell, k^k \})$-competitive.

@@

Algorithm Alg:
\mahmoud{find a better name for Alg.}
maintain a counter $C_{\set{u,v}}$ for each pair of nodes $\set{u,v}$ and increment it on every remote request between $u$ and $v$.
Once $C_{\set{u,v}} = \lambda$,
reset the counter and collocate the pair arbitrarily in one of the two clusters where $u$ or $v$ resides.

\begin{theorem} \label{thm:k=2}
	The algorithm, for $\lambda=\alpha$, is (strictly) 6-competitive.
\end{theorem}

We charge both OPT and Alg whenever Alg collocates a pair (i.e., on a collocation event).
%More precisely,we charge them only the cost of the collocation, per such event.
%Hence,we charge the cost of  this collocation to OPT for the first time.
Alg collocates a pair always with a swap (i.e., two simultaneous migrations),
which  costs $2\alpha$.
%We charge OPT only for requests up to the one that triggers a collocation (i.e., not for later requests on the same pair).
OPT may save some costs by collocating multiple pairs at once (before they incur too much cost),
paying the price of only one migration per pair  (\mahmoud{see Figure \ref{fig:TBD}}).
%This observation suggests that we can't charge OPT more than $\alpha$ per collocation.
%E.g.,
%OPT can collocate two costly pairs with a single swap if
%it has both pairs on the cut of  the same two clusters.
%Later, Alg collocates those pairs with two swaps.
Hence,
whenever OPT collocates a pair,
we charge it only the cost of moving a single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ on Alg).

Assume on request $\sigma_{t}=\set{u,v}$, 
i.e., at (time) $t$,
Alg collocates the pair $\set{u,v}$.
This means,
the value of $C_{\set{u,v}}$ at $t$,
denoted by $C^t_{\set{u,v}}$, 
reaches $\lambda$ immediately before Alg resets the counter.
I.e.,
$ C^t_{\set{u,v}} = \lambda$.
%	In case the first collocation of $\set{u,v}$ occurs at $t$,
%	if the pair is collocated in the initial configuration then
%	we set $t''=0$,
%	else,
%	we set $ t'' = -\infty, t'=0$.
We denote the set of all requests to a pair $\set{x,y}$ that arrive
during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
and its overall cost to OPT by
$\mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}[t_1,t_2])$.
%
%Else, this is not the first time and
%Alg collocates $\{u,v\}$ also some time prior to $t$.

If $t$ is not the first time that Alg collocates $\{u,v\}$ then
let $0 < t' < t$ be the latest time when Alg separates $\set{u,v}$
in order to collocate some (intersecting) pair
$\{x,y\} \neq \{u,v\}, \{x,y\} \cap \{u,v\} \neq \emptyset$, 
e.g.,
$\{x,y\}=\{u,v'\}$.
Else,
$t$ is the first time that Alg collocates $\{u,v\}$ and let $t' := 0$.
Similarly,
if $t' > 0$ is not the first time that Alg  collocates $\{u,v'\}$ 
then let $0 < t'' < t'$ be the latest time before $t'$ when Alg separates $\set{u,v'}$.
Else,
$t'$ is the first time that Alg collocates $\{u,v'\}$ and we let $t''=0$.
%

Observe that for requests in
$R_t := \sigma_{\{u,v'\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t]$ 
and the entire duration of the input sequence (i.e., $(0,m]$),
OPT must pay a total cost
%We denote the cost w.r.t~$r_t$ by
$\mathit{Cost}_{\mathit{OPT}} (R_t) \geq 
	c_{R_t} := \min{ \{ 2\lambda, \lambda+\alpha, 2\alpha \} }$,
for serving (some of) these requests remotely or (and) collocating (one of) the pairs,
regardless of its choices.
Then the cost per pair, in particular the cost w.r.t.~$\{u,v\}$, is
$\mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}(t',t]) \geq c_{R_t} / 2$.
%
However,
we can charge this cost to OPT only at $t=t_0$,
i.e.~the first time Alg collocates $\{u,v\}$,
and not at any consequent time $\tilde{t} > t_0$ that Alg collocates $\{u,v\}$.
%	i.e.,
%	when Alg collocates the two pairs a second time.
That is,
we charge OPT a cost incurred by requests in
$\sigma_{\{u,v'\}}(t'',t']$ or $\sigma_{\{u,v\}}(t',t]$,
if and only if  OPT incurs the cost during  intervals $(t'', t']$ or $(t', t]$,
respectively.	
Latter,
this ensures us that we do not charge OPT for a cost more than twice.
%%
We use notations defined so far in the proof that follows.

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	First,
	we bound the costs incurred by Alg for requests that
	lead to the collocation of $\{u,v\}$ at time $t \in T$, where
	$T := \{ i \in [1,m] ~\vert~ \exists \{x,y\}: C^{i}_{\{x,y\}} = \lambda \}$.
	By definitions of $t$ and $t'$,
	the overall cost of requests in $\sigma_{\set{u,v}}(t',t]$ incurred by Alg,
	i.e., the total cost of remote serving
	and the moving cost, is
	$\lambda + 2\alpha$.	
	Next,
	we bound the cost incurred by Alg
	for requests that do not lead to collocations until the  end of the sequence at $t=m$.
	Assume $\{u,v\}$ is not collocated at $t=m$
	and $0 < C^{m}_{ \{u,v\} } < \lambda $,
	which means Alg pays $C^{m}_{ \{u,v\} }$
	for these requests $\sigma_{\set{u,v}}(t',m]$.
    Then the overall cost to Alg is

	\begin{align*}	%\label{eq:costAlg}
	\mathit{Cost}_{\mathit{ALG}} (\sigma)
	=
	\sum_{ t \in T}(\lambda + 2\alpha) +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}	
	\leq
	\sum_{ t \in T}(\lambda + 2\alpha) +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}	
	=
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	.
	\end{align*}

	Next,
	we bound  costs incurred by OPT	for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that Alg collocates $\{u,v\}$ then  OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with cost 0.
	Therefore in this case,
	OPT pays
	$\mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	By these definitions,
	we have
	$| \sigma_{\set{u,v'}}(t'',t'] | = | \sigma_{\set{u,v}}(t',t] |  =  \lambda$.
	For requests $R_t := \sigma_{\set{u,v'}}(t'',t']  \cup \sigma_{\set{u,v}}(t',t]$,
	OPT pays
	$\mathit{Cost}_{\mathit{OPT}} (R_t) := \mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v'\}}(t'',t']) 
	+ \mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}(t',t]) $.
	We distinguish three (non-exhaustive) cases for the cost to OPT.
	Latter,
	 we argue that OPT cannot save cost by deviating from these cases.
	\begin{enumerate}[label=\roman*.]
		\item
		OPT collocates $\{u,v'\}$ at  $t''$, $\{u,v\}$  at $t'$,
		and keeps them so during $(t'',t']$ and $(t',t]$, respectively.
		Therefore it serves all requests in $R_t$ with no additional cost and
		$ c_1 (R_t) := 2\alpha$.
		\item
		OPT has $\{u,v\}$ ($\{u,v'\}$) already collocated at $t'$ ($t''$) as well as during $(t',t]$ ($(t'',t]$),
		and has $\{u,v'\}$ ($\{u,v\}$) separated during $(t'',t']$ ($(t',t]$).
		Hence,
		it pays only $\lambda$ for serving all requests in $R_t$ and
		$c_2 (R_t) := \lambda$
		\item
		OPT has $\{u,v'\}$ ($\{u,v\}$) already collocated at $t''$ ($t'$)  and also during $(t'',t']$ ($(t', t])$.
		Then it pays 0 for $\sigma_{\{u,v'\}}[t'',t']$ ($(\sigma_{\{u,v\}}[t',t]$), and
		$c_3 (R_t) := \alpha$.
	\end{enumerate}
	If OPT's choice is one of these cases,
	then
	$\mathit{Cost}_{\mathit{OPT}} (R_t) \geq
		\min{\{ c_1(R_t), c_2(R_t), c_3(R_t) \}}  =
		\min{ \{ \lambda, \alpha \}}$.
	Otherwise,
	OPT deviates from these cases,
	e.g.~by collocating a pair after paying for some of requests to this pair.
	However,
	no deviation can decrease the cost to OPT.
	Therefore in any case,
	$\mathit{Cost}_{\mathit{OPT}} (R_t) \geq  \min{ \{ \lambda, \alpha \}}$.

	It remains to bound the cost  incurred by OPT for requests to $\{u,v\}$ that do not lead to its collocation until the end of the sequence at $t=m$.
	If $\{u,v\}$ is not collocated in the initial configuration
	and Alg never collocates it,
	then $ C^{m}_{ \{u,v\} } =| \sigma_{\{u,v\}}[1,m] |$.
	OPT pays
	$\mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}[1,m]) 
	\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
	for collocating this pair or (and) paying for (some of) requests in $\sigma_{\{u,v\}}[1,m]$.
	Else,
	either $\{u,v\}$ is collocated in the initial configuration
	or Alg collocates it at some point.
	Then there exists an intersecting pair $\set{u,v'}$
	that is collocated by Alg at $t' < m$ (separating $\{u,v\}$).
	We define times $t'' < t' < m$ similarly to the case where Alg collocates $\{u,v\}$.
	Let $R_{\{u,v\}} := \sigma_{\{u,v'\}} (t'',t'] \cup \sigma_{\{u,v\}} (t',m]$.
	Then,
	we apply cases (i) to (iii) in an analogous way,
	replacing $\lambda$ with $C^{m}_{ \{u,v\}}$ in the analysis.
	Thus, 
	we obtain
	$\mathit{Cost}_{\mathit{OPT}} (R_{\{u,v\}}) 
	\geq  \min{ \{ C^{m}_{ \{u,v\}}, \alpha \}}$.

	Next, we sum up all costs incurred by OPT.
	By definitions of $R_t$ and $R_{\{u,v\}}$, we have either
	$R_{t'} \cap R_t = \sigma_{\{u,v'\}}[t'',t']$ or
	$R_{t'} \cap R_{\{u,v\}} = \sigma_{\{u,v'\}}[t'',t']$
	(\mahmoud{See figure \ref{fig:doubleCount}}). 
	This means,
	$\mathit{Cost}_{OPT} ( \sigma_{\{u,v'\}}[t'',t'])$
	is counted at most twice in each of  the expressions
	$\mathit{Cost}_{\mathit{OPT}} (R_{t'}) + \mathit{Cost}_{\mathit{OPT}} (R_t)$
	and  
	$\mathit{Cost}_{\mathit{OPT}} (R_{t'}) + \mathit{Cost}_{\mathit{OPT}} (R_{\{u,v\}})$.
	Hence,
	for all collocations performed by Alg,
	and for final costs at $t=m$,
	OPT pays at least 
	$\frac{1}{2}(
	\sum_{ t \in [1,m] } \mathit{Cost}_{\mathit{OPT}} (R_t) +
	\sum_{\{u,v\}} \mathit{Cost}_{\mathit{OPT}} (R_{\{u,v\}})
	) $.
	Then,
	the total cost to OPT is

	\begin{align*} 	%\label{eq:costOPT}
		\mathit{Cost}_{\mathit{OPT}} (\sigma)
		&=
		\frac{1}{2}
		\Big(
		\sum_{ t \in T} \mathit{Cost}_{\mathit{OPT}} (R_t) 
		+ \sum_{\{u,v\}}\mathit{Cost}_{\mathit{OPT}} (R_{\{u,v\}})
		\Big)	\\
		&\leq
		\Big(
		\sum_{ t \in T} \min{ \{ \lambda, \alpha \}}  +
		\sum_{\{u,v\}} \min{ \{C^{m}_{\{u,v\}} , \alpha \} } 
		\Big)		
		=
		\frac{1}{2}		
		\Big(
		\sum_{ t \in T} \alpha  
		+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}
		\Big).
	\end{align*}

@@

\begin{align*}
	\mathit{Cost}_{\mathit{ALG}} (\sigma)	/
	\mathit{Cost}_{\mathit{OPT}} (\sigma)
	\leq
	2\Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  
	\Big)	< 6.
\end{align*}
%	The claim follows from here.

@@

\maciek{I feel slightly uneasy here: "In particular,
we charge OPT a cost incurred by requests in
$\sigma_{\{u,v'\}}(t'',t']$ and $\sigma_{\{u,v\}}(t',t]$,
if and only if  OPT incurs the cost within  intervals $(t'', t']$ and $(t', t]$,
respectively.
\mahmoud{this is only for intuition but a key statement. It is meant to say: OPT may pay cost for the same two pairs outside the intervals. But we don't charge OPT  those costs at $t$. This way we avoid over charging OPT as only intervals $r_{t'}$ and $r_t$ can overlap which leads to double charging and we take care of it.}
"}

@@

\maciek{"We charge OPT the cost
$\mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}[1,t]) 
\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
for collocating this pair or (and) paying (partially) for requests in $\sigma_{\{u,v\}}[1,t]$." No issues with charge sharing from "regular collocation" case? Maybe I just don't understand "partially" here. Not necessarily rewrite! Just maybe check if it's true.
\mahmoud{this is the cost of first collocation of $\{u,v\}$. "partially" is confusing and now it says "some of" instead.}}

@@

\maciek{The big inequality is impressive, but not a lot change in each row. Instead, bound the cost of ALG separately in one line, and the cost of OPT in another. (possibly far away from eachother) \mahmoud{done}}

@@

\maciek{Structure in paragraphs. 3 parts: first collocation, regular collocation and unfinished. Do this for ALG and then for OPT, and do not mix (unless I don't see some dependencies). Start each paragraph by the sentence that says what the paragraph is about (first/opt, regular/alg etc.). Assume that the reader reads only the first sentence of each paragraph (if it's short), and the proof structure must be clear from this. Some other important things go to their own paragraph too, and the first sentence must describe what we do there.}

\maciek{$R_t$ is the central concept in this proof. Possibly even start with the paragraph: charging OPT, regular collocation. Make this definition in its separate line to further emphasize? It would suffice for a profesional to see the definiton of $t''/t'$ and this line to convince himself that the proof is correct.}

@@

\begin{comment}
	We charge both OPT and Alg whenever Alg collocates a pair (i.e., on a collocation event).
	%More precisely,we charge them only the cost of the collocation, per such event.
	%Hence,we charge the cost of  this collocation to OPT for the first time.
	Alg collocates a pair always with a swap (i.e., two simultaneous migrations),
	which  costs $2\alpha$.
	%We charge OPT only for requests up to the one that triggers a collocation (i.e., not for later requests on the same pair).
	OPT may save some costs by collocating multiple pairs at once (before they incur too much cost),
	paying the price of only one migration per pair.
	This observation suggests that we can't charge OPT more than $\alpha$ per collocation,
	even when OPT actually pays more than that.
	E.g.,
	OPT can collocate two costly pairs with a single swap if
	it has both pairs on the cut of  the same two clusters.
	Later, Alg collocates those pairs with two swaps (see Figure \ref{fig:TBD}).
	Hence,
	whenever OPT collocates a pair,
	we charge OPT only the cost of moving a single node to the cluster of the other,
	i.e., $\alpha$ (in contrast to $2\alpha$ for Alg).

	\begin{proof}[Proof of Theorem \ref{thm:k=2}]
		\mahmoud{not correct}
		%	Let $C^{t}_{\set{u,v}}$ denote the  value of $C_{\set{u,v}}$
		%	immediately after arrival of the $t$th request,
		%	$\sigma_t$.
		Assume on request $\sigma_{t}=\set{u,v}$, 
		i.e., at (time) $t \geq 1$,
		Alg collocates the pair $\set{u,v}$.
		This means,
		the value of $C_{\set{u,v}}$ at $t$,
		immediately before Alg resets the counter is $\lambda$.
		That is, $ C^t_{\set{u,v}} = \lambda$.
		Let $\sigma_{t''}, t''<t$ be the last request (before $\sigma_{t}$)
		upon which Alg collocates $\set{u,v}$.
		Let $t'$, $t'' < t' < t$ be the  time when Alg separates $\set{u,v}$
		in order to collocate some other pair that shares a node with $\set{u,v}$,
		e.g.~$\set{u,v'}, v' \neq v$.
		In case the first collocation of $\set{u,v}$ occurs at $t$,
		if the pair is collocated in the initial configuration then
		we set $t''=0$,
		else,
		we set $ t'' = -\infty, t'=0$.
		We denote the set of all requests to $\set{u,v}$
		during $[t_1,t_2]$ by $\sigma_{\set{u,v}}[t_1,t_2]$.
		Thus,
		$| \sigma_{\set{u,v}}[t',t] | = \lambda$.
		The overall cost of requests that increase the counters of intersecting pairs,
		%	i.e.~requests in $\sigma_{\set{u,v}}[t'',t]$,
		and the moving cost,
		incurred by Alg is
		$\lambda + 2\alpha$.
		%That is, the cost of all requests in $\sigma_{\set{u,v}}[t',t]$.

		We distinguish three cases for the cost incurred by OPT with respect to the collocation of $\set{u,v}$ at $t$.

		\begin{enumerate}
			\item Case i)
			OPT has $\set{u,v}$ separated (in OPT's configuration) during $[t',t]$
			and therefore it pays $\lambda$.
			We charge OPT $\lambda/2$, i.e.,
			$\mathit{Cost}^{t}_{\{u,v\}} (\mathit{OPT})= \lambda / 2$.

			\item Case ii)  
			OPT collocates $\set{u,v}$ some time during $[t'',t]$ and pays $\alpha$.
			We charge it $\alpha/2$, i.e.,
			$\mathit{Cost}^{t}_{\{u,v\}} (\mathit{OPT}) = \alpha / 2$.

>>>>

 \newcommand{\OPT}{\textsf{OPT}\xspace}
 \newcommand{\ALG}{\textsf{ALG}\xspace}
 \newcommand{\PPL}{\textsf{PPL}\xspace}
 \newcommand{\OBRP}{BRP}
 \newcommand{\PPOBRP}{PP-BRP}
 \newcommand{\dist}{\textsf{dist}}
 \newcommand{\TAlg}{{\ensuremath{\textsf{ALG}_{3}}}\xspace}
  \newcommand{\RM}{\textsf{RM}\xspace} % rematching alg

@@

@@

\begin{comment}
\section{Bounding the cost of a single reconfiguration of components}

@@

Corollary: Algorithm DET2 is $O(\ell \cdot k \cdot \min \{ \ell, k^k \})$-competitive.
\end{comment}

@@

We describe the algorithm \RM for the online rematching problem as follows.
The input to \RM is a sequence of  requests
$\sigma:=\{\sigma_1,\dots, \sigma_m\}, \sigma_t:=\{x,y\} \in V^2, x \neq y$.
We maintain a counter $C_{\set{x,y}}$ for each pair of nodes $\set{x,y}$ and increment it on every remote request between $x$ and $y$.
Once $C_{\set{x,y}} = \lambda$,
reset the counter and collocate the pair arbitrarily in one of the two clusters where $x$ or $y$ resides.

\begin{theorem} \label{thm:k=2}
	The algorithm \RM, for $\lambda=\alpha$, is (strictly) 6-competitive.
\end{theorem}

We charge both \OPT and \RM whenever \RM collocates a pair (i.e., on a collocation event).
%More precisely,we charge them only the cost of the collocation, per such event.
%Hence,we charge the cost of  this collocation to \OPT for the first time.
Alg collocates a pair always with a swap (i.e., two simultaneous migrations),
which  costs $2\alpha$.
%We charge \OPT only for requests up to the one that triggers a collocation (i.e., not for later requests on the same pair).
OPT may save some costs by collocating multiple pairs at once (before they incur too much cost),
paying the price of only one migration per pair  (\mahmoud{see Figure \ref{fig:TBD}}).
%This observation suggests that we can't charge \OPT more than $\alpha$ per collocation.
%E.g.,
%OPT can collocate two costly pairs with a single swap if
%it has both pairs on the cut of  the same two clusters.
%Later, \RM collocates those pairs with two swaps.
Hence,
whenever \OPT collocates a pair,
we charge it only the cost of moving a single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ on Alg).

Observe that for requests in
$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $ 
and the entire duration of the input sequence (i.e., $(0,m]$),
OPT must pay a total cost
%We denote the cost w.r.t~$r_t$ by
$\mathit{OPT} (R_t) \geq 
	c_{R_t} := \min{ \{ 2\lambda, \lambda+\alpha, 2\alpha \} }$,
for serving (some of) these requests remotely or (and) collocating (one of) the pairs,
regardless of its choices.
Then the cost per pair, in particular the cost w.r.t.~$\{u,v\}$, is
$\mathit{OPT} (\sigma_{\{u,v\}}) \geq c_{R_t} / 2$.
%
However,
we can charge this cost to \OPT only at $t=t_0$,
i.e.~the first time \RM collocates $\{u,v\}$,
and not at any consequent time that \RM collocates $\{u,v\}$.
That is,
we charge \OPT a cost incurred by requests in
$\sigma_{\{u,w\}}$ or $\sigma_{\{u,v\}}$,
if and only if  \OPT incurs the cost during  intervals $(t'', t']$ or $(t', t]$,
respectively.	
Latter,
this ensures us that we do not charge \OPT for a cost more than twice.
%%
We use notations defined so far in the proof that follows.

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	Alg collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter.
	I.e.,
	$ C^t_{\set{u,v}} = \lambda$.
	%	In case the first collocation of $\set{u,v}$ occurs at $t$,
	%	if the pair is collocated in the initial configuration then
	%	we set $t''=0$,
	%	else,
	%	we set $ t'' = -\infty, t'=0$.
	We denote the set of all requests to a pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
	and its overall cost to \OPT by
	$\mathit{OPT} (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.

	If $t$ is not the first time that \RM collocates $\{u,v\}$ then
	let $0 < t' < t$ be the latest time when \RM separates $\set{u,v}$
	in order to collocate some (intersecting) pair
	$\{x,y\} \neq \{u,v\}, \{x,y\} \cap \{u,v\} \neq \emptyset$, 
	e.g.,
	$\{x,y\}=\{u,w\}$.
	Else,
	$t$ is the first time that \RM collocates $\{u,v\}$ and let $t' := 0$.
	Similarly,
	if $t' > 0$ is not the first time that \RM  collocates $\{u,w\}$ 
	then let $0 < t'' < t'$ be the latest time before $t'$ when \RM separates $\set{u,w}$.
	Else,
	$t'$ is the first time that \RM collocates $\{u,w\}$ and we let $t''=0$.
	%

	First,
	we bound the costs incurred by \RM for requests that
	lead to the collocation of $\{u,v\}$ at time $t \in T$, where
	$T := \{ i \in [1,m] ~\vert~ \exists \{x,y\}: C^{i}_{\{x,y\}} = \lambda \}$
	is the set of times when \RM performs a collocation.
	By definitions of $t$ and $t'$,
	the overall cost of requests in $\sigma_{\set{u,v}}$ incurred by Alg,
	i.e., the total cost of remote serving
	and the moving cost, is
	$\lambda + 2\alpha$.	
	Next,
	we bound the cost incurred by Alg
	for requests that do not lead to collocations until the  end of the sequence at $t=m$.
	Assume $\{u,v\}$ is not collocated at $t=m$
	and $0 < C^{m}_{ \{u,v\} } < \lambda $,
	which means \RM pays $C^{m}_{ \{u,v\} }$
	for these requests $\sigma_{\set{u,v}}(t',m]$.
    Then the overall cost to \RM is

	\begin{align*}	%\label{eq:costAlg}
	\mathit{ALG} (\sigma)
	=
	\sum_{ t \in T}(\lambda + 2\alpha) +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}	
	\leq
	\sum_{ t \in T}(\lambda + 2\alpha) +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}	
	=
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	.
	\end{align*}

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$ then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with cost 0.
	Therefore in this case,
	$\mathit{OPT} (\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as define previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$ in an analogous way.
	Then,
	$\mathit{OPT} (R_t) = \mathit{OPT} (\sigma_{\{u,w\}}) 
	+ \mathit{OPT} (\sigma_{\{u,v\}}) $.
	We distinguish three (non-exhaustive) cases for the cost to \OPT w.r.t.~$R_t$.
	Latter,
	 we argue that \OPT cannot save cost by deviating from these cases.
	\begin{enumerate}[label=\roman*.]
		\item
		\OPT collocates $\{u,w\}$ at  $t''$, $\{u,v\}$  at $t'$,
		and keeps them so during $(t'',t']$ and $(t',t]$, respectively.
		Therefore it serves all requests in $R_t$ with no additional cost and
		let $\OPT_1 (R_t) := 2\alpha$.
		\item
		\OPT has one of the pairs  already collocated and the other pair separated,
			  prior to and during their respective intervals.
		Hence,
		it pays only $\lambda$ for serving all requests in $R_t$
		and let $\OPT_2 (R_t) := \lambda$.
		\item
		\OPT has one of the pairs already collocated prior to its interval,
		and it collocates the other pair during the respective interval.
		Then it pays 0 for one pair and $\alpha$ for the other and 
		let $\OPT_3 (R_t) := \alpha$.
	\end{enumerate}
%	We consider cases (ii) and (iii) also for the pair $\{u,w\}$, symmetrically.
	If \OPT behaves in one of these cases,
	then
	$\mathit{OPT} (R_t) \geq
		\min{\{ \OPT_1(R_t), \OPT_2(R_t), \OPT_3(R_t) \}}  =
		\min{ \{ \lambda, \alpha \}}$.
	Otherwise,
	\OPT deviates from these cases,
	e.g.~by collocating a pair after paying for some of requests to this pair.
	However,
	no deviation can decrease the cost to \OPT. \mahmoud{prove this!}
	Therefore in any case,
	$\mathit{OPT} (R_t) \geq  \min{ \{ \lambda, \alpha \}}$.

	It remains to bound the cost  incurred by \OPT for requests to $\{u,v\}$ that do not lead to its collocation until the end of the sequence at $t=m$.
	If $\{u,v\}$ is not collocated in the initial matching
	and \RM never collocates it,
	then $ C^{m}_{ \{u,v\} } =| \sigma_{\{u,v\}}[1,m] |$.
	\OPT pays
	$\mathit{OPT} (\sigma_{\{u,v\}}[1,m]) 
	\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
	for collocating this pair or (and) paying for (some of) requests in $\sigma_{\{u,v\}}[1,m]$.
	Else,
	either $\{u,v\}$ is collocated in the initial matching
	or \RM collocates it at some point.
	Then there exists an intersecting pair $\set{u,w}$
	that is collocated by \RM at $t' < m$ (separating $\{u,v\}$).
	We define times $t'' < t' < m$ similarly to the case where \RM collocates $\{u,v\}$.
	Let $R^*_{\{u,v\}} := \sigma_{\{u,w\}} (t'',t'] \cup \sigma_{\{u,v\}} (t',m]$.
	Then,
	we apply cases (i) to (iii) in an analogous way,
	replacing $\lambda$ with $C^{m}_{ \{u,v\}}$ in the analysis.
	Thus, 
	we obtain
	$\mathit{OPT} (R^*_{\{u,v\}}) 
	\geq  \min{ \{ C^{m}_{ \{u,v\}}, \alpha \}}$.

	Next, we sum up all costs incurred by \OPT.
	By definitions of $R_t$ and $R^*_{\{u,v\}}$, we have either
	$R_{t'} \cap R_t = \sigma_{\{u,w\}}$ or
	$R_{t'} \cap R^*_{\{u,v\}} = \sigma_{\{u,w\}}$
	(\mahmoud{See figure \ref{fig:doubleCount}}). 
	This means,
	$\mathit{Cost}_{OPT} ( \sigma_{\{u,w\}})$
	is counted at most twice in each of  the expressions
	$\mathit{OPT} (R_{t'}) + \mathit{OPT} (R_t)$
	and  
	$\mathit{OPT} (R_{t'}) + \mathit{OPT} (R^*_{\{u,v\}})$.
	Hence,
	for all collocations performed by Alg,
	and for final costs at $t=m$,
	\OPT pays at least 
	$\frac{1}{2}(
	\sum_{ t \in [1,m] } \mathit{OPT} (R_t) +
	\sum_{\{u,v\}} \mathit{OPT} (R^*_{\{u,v\}})
	) $.
	Then,
	the total cost to \OPT is

	\begin{align*} 	%\label{eq:costOPT}
		\mathit{OPT} (\sigma)
		&=
		\frac{1}{2}
		\Big(
		\sum_{ t \in T} \mathit{OPT} (R_t) 
		+ \sum_{\{u,v\}}\mathit{OPT} (R^*_{\{u,v\}})
		\Big)	\\
		&\leq
		\Big(
		\sum_{ t \in T} \min{ \{ \lambda, \alpha \}}  +
		\sum_{\{u,v\}} \min{ \{C^{m}_{\{u,v\}} , \alpha \} } 
		\Big)		
		=
		\frac{1}{2}		
		\Big(
		\sum_{ t \in T} \alpha  
		+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}
		\Big).
	\end{align*}

@@

\begin{align*}
	\mathit{ALG} (\sigma)	/
	\mathit{OPT} (\sigma)
	\leq
	2\Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  
	\Big)	< 6.
\end{align*}
%	The claim follows from here.

@@

\maciek{I feel slightly uneasy here: "In particular,
we charge \OPT a cost incurred by requests in
$\sigma_{\{u,w\}}$ and $\sigma_{\{u,v\}}$,
if and only if  \OPT incurs the cost within  intervals $(t'', t']$ and $(t', t]$,
respectively.
\mahmoud{this is only for intuition but a key statement. It is meant to say: \OPT may pay cost for the same two pairs outside the intervals. But we don't charge \OPT  those costs at $t$. This way we avoid over charging \OPT as only intervals $r_{t'}$ and $r_t$ can overlap which leads to double charging and we take care of it.}
"}

@@

\maciek{"We charge \OPT the cost
$\mathit{\OPT} (\sigma_{\{u,v\}}[1,t]) 
\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
for collocating this pair or (and) paying (partially) for requests in $\sigma_{\{u,v\}}[1,t]$." No issues with charge sharing from "regular collocation" case? Maybe I just don't understand "partially" here. Not necessarily rewrite! Just maybe check if it's true.
\mahmoud{this is the cost of first collocation of $\{u,v\}$. "partially" is confusing and now it says "some of" instead.}}

@@

\maciek{The big inequality is impressive, but not a lot change in each row. Instead, bound the cost of ALG separately in one line, and the cost of \OPT in another. (possibly far away from eachother) \mahmoud{done}}

@@

\maciek{Structure in paragraphs. 3 parts: first collocation, regular collocation and unfinished. Do this for ALG and then for \OPT, and do not mix (unless I don't see some dependencies). Start each paragraph by the sentence that says what the paragraph is about (first/opt, regular/alg etc.). Assume that the reader reads only the first sentence of each paragraph (if it's short), and the proof structure must be clear from this. Some other important things go to their own paragraph too, and the first sentence must describe what we do there.}

\maciek{$R_t$ is the central concept in this proof. Possibly even start with the paragraph: charging \OPT, regular collocation. Make this definition in its separate line to further emphasize? It would suffice for a profesional to see the definiton of $t''/t'$ and this line to convince himself that the proof is correct.}

@@
